%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{André}}}}} % First name
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Fernandes}}}}} % Last name
	\vspace{6pt}
 
	{\fontsize{15}{15} \selectfont Software Developer} % Career or current job title
 
\end{minipage}
\hfill
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons 
	\icon{MapMarker}{12}{Florianópolis - SC}
	
	\icon{Phone}{12}{+55 (48) 991 673 945}
 
	\icon{At}{12}{\href{mailto:fpf.andre@gmail.com}{fpf.andre@gmail.com}}
 
	\icon{Github}{12}{\href{https://github.com/andrefpf}{github.com/andrefpf}}
\end{minipage}

\vspace{0.5cm}


%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2023 -- Today}
		{Software Developer}
		{Laboratório de Vibrações e Acústica (LVA) - UFSC}
		{
			Desenvolvimento de softwares de engenharia para simulação de pulsação acusticamente induzida em tubulações para Petrobrás utilizando Python. 
			
			\texttt{Python} / \texttt{Git} / \texttt{PyQt} / \texttt{VTK} / \texttt{Matplotlib}
		}

	\entry
		{2023 -- Today \\ \footnotesize{Volunteer}}
		{Scientific initiation fellow}
		{Embedded Computing Lab (ECL) - UFSC}
		{
			Development of algorithms to solve the target rate problem in light fields coded by the 4D Transform Mode according to the JPEG Pleno standard.

			\texttt{Python} / \texttt{Git} / \texttt{PyQt} / \texttt{VTK} / \texttt{Matplotlib}
		}

	\entry
		{2022 -- 2023 \\ \footnotesize{part time}}
		{Backend Developer Trainee}
		{Cognyte}
		{
			Development of Rest API's to integrate microservices, updating of legacy codebases to modern C++ and bug fixing.
            
            \texttt{C++} / \texttt{Python} / \texttt{Git} / \texttt{Docker} / \texttt{Boost}
        }
	\entry
		{2019 -- 2022\\\footnotesize{part time}}
		{Python Developer}
		{Laboratório de Vibrações e Acústica (LVA) - UFSC}
		{
			Development of enginering softwares for simulation of acoustic pulsation in process unit pipelines. Project developed in partnership with Petrobras.
            
            \texttt{Python} / \texttt{Git} / \texttt{PyQt} / \texttt{VTK} / \texttt{Matplotlib}
        }
	\entry
		{2017 -- 2018 \\ \footnotesize{part time}}
		{Adiministrative Assistant}
		{NSC TV}
		{
            NSC TV is a corporation affiliated to Globo, the biggest broadcasting corporation in Brazil. NSC TV covers the state of Santa Catarina. 
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2019 -- 2024}
		{Bachelor in Computer Science}
		{\\Universidade Federal de Santa Catarina - UFSC}
		{
			Method to solve the target rate problem in Light Fields encoding according to JPEG Pleno Part 2 - 4DTM standard.
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Languages}
 
	\textbf{Portuguese} - Native \\
	\textbf{English} - Fluent
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Technologies}
 
    Python\\
    C++\\
    Javascript\\
	Rust\\
    Git\\
    Docker\\
    
    
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Topics of Interest}
 
    Data Encoding\\
    Computer Graphics\\
    Phisics Simulation\\
	Formal Languages\\
    Open Source
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
